---
title: "Report"
author: "Eric R. Scott"
date: "2022-10-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exploratory data analysis

Does it look like seedlings differ in height in different watersheds?

```{r}
tar_read(plot_boxplot)
```

In both years it looks like seedlings were taller in calcium treated watersheds

## Summary Statistics

```{r}
tar_read(tbl_summary)
```


# Modeling

We can fit a model to test if there is a relationship between seedling mass and stem height, and if that slope differs by watershed.

```{r echo=FALSE,render='asis'}
library(equatiomatic)
extract_eq(tar_read(stem_lm))
```

# Results

There is strong evidence for a relationship between stem length and mass (p < 0.001), an effect of watershed (p < 0.001) with plants in the calcium-treated watersheds being taller, but no significant interaction (p = 0.07) indicating no difference in slope by watershed.

```{r}
tar_read(stem_anova) %>% knitr::kable()
```


```{r}
tar_read(plot_model)
```

